Bird beak's elaboration and exploration

### 2022-05-31 Analysis/02-mcmcmcglmmm_analysis.Rmd
Update 02-mcmcmcglmmm_analysis.Rmd

## Loading the parametrisation data
load(file = "../Data/Processed/shapsepace_passeriformes_suborder_family.rda")

## Select the data
shapespace <- shapsepace_passeriformes_suborder_family[[1]]$space
selected_dim <- shapsepace_passeriformes_suborder_family[[1]]$dimensions
consensus_tree <- shapsepace_passeriformes_suborder_family[[1]]$consensus_tree
trees_list <- shapsepace_passeriformes_suborder_family[[1]]$trees_list
```

@@

```{r, parametrise_the_model, eval = FALSE}
## Set up the parametrising chains models
param_MCMCglmm <- make.mini.chains(data         = shapespace,
                                   dimensions   = selected_dim,
                                   tree         = consensus_tree,
                                   trait.family = "gaussian",
                                   randoms      = c("global", "level1", "level2"),
                                   residuals    = "global",
                                   priors       = 0.02,
                                   verbose      = TRUE,
                                   parameters   = list(
                                       nitt   = 50000,
                                       thin   = 500,
                                       burnin = 0))

## Running the three MCMCglmm models
save(param_chains, file = "../Data/Processed/MCMCglmm/params_shapespace_8D_29levels_5k_chain1.rda")
```

>>>>

## Loading the parametrisation data
load(file = "../Data/Processed/shapespace_passeriformes_suborder_family.rda")

## Select the data
shapespace <- shapespace_passeriformes_suborder_family[[1]]$space
selected_dim <- shapespace_passeriformes_suborder_family[[1]]$dimensions
consensus_tree <- shapespace_passeriformes_suborder_family[[1]]$consensus_tree
trees_list <- shapespace_passeriformes_suborder_family[[1]]$trees_list
```

@@

```{r, parametrise_the_model, eval = FALSE}
## Set up the parametrising chains models
param_chains <- make.mini.chains(data         = shapespace,
                                   dimensions   = selected_dim,
                                   tree         = consensus_tree,
                                   trait.family = "gaussian",
                                   randoms      = c("global", "level1", "level2"),
                                   residuals    = "global",
                                   priors       = 0.02,
                                   verbose      = TRUE,
                                   parameters   = list(
                                       nitt   = 50000,
                                       thin   = 500,
                                       burnin = 0))

# Running the three MCMCglmm models
save(param_chains, file = "../Data/Processed/params_shapespace_8D_50levels_50k_chain1.rda")
```
